### 2014-11-07 appendix.tex
Techreport is a separate file

\subsection{Axiomatic Semantics}
\renewcommand{\auxred}[4]{#1 \vdash #2 \;\xhookrightarrow{#3}\; #4 }

We now describe axiomatic semantics of a data store that implements
strong, causal and eventual consistency guarantees. The semantics also
serves as an elegant representation of our implementation of \name.

@@

The state of an axiomatic execution ($\E$) is a tuple $\Exec$ where $\EffSoup$
is a set of effects, and $\visZ,\soZ, \sameobjZ \subseteq \EffSoup \times
\EffSoup$ are \emph{visibility}, \emph{session order}, and \emph{same object}
relations over effects, respectively. We concretize an effect ($\eff$) as a
tuple $(s,i,op,v)$, which records the fact that $i^{th}$ action in session
with {\sf SessID} $s$, which is an operation $op$ on the replicated object,
has been successfully executed on some replica yielding a return value $v$.
Note that the combination of $s$ and $i$ uniquely identifies the effect.
Session order relation ($\soZ$) relates effects generated by the same session.
An effect $\eff = (s,i,op,v)$ is said to precede another effect $\eff' =
(s',i',op',v')$ in session order if and only if $s'=s$ and $i'\ge i$. Since we
only consider one replicated object in our formalization, the $\sameobjZ$
relation relates every pair of effects in the effect soup ($\EffSoup$). An
effect generated at a replica becomes visible at rest of the replicas
eventually.  If we denote the effect generated by the operation $op$ as
$\eff_{op}$, then $\Theta(r) \times \{\eff_{op}\} ~\subseteq~ \visZ$. Often,
in our formalization, we use $\visZ$ and $\soZ$ binary relations to obtain a
set of effects visible to a given effect $\eff$, or set of effects that
precede a given effect $\eff$ in the session order. As a syntactic
convenience, whenever $R$ is a binary relation, we write $R(\eff)$ to denote
the set of all $\eff'$ such that $(\eff,\eff') \in R$.  Conversely, we write
$R^{-1}(\eff)$ to denote the set of all $\eff'$ such that $(\eff',\eff) \in
R$.

@@

\subsection{Soundness of Axiomatic Semantics}

Our main meta-theoretic result guarantees the soundness of our
axiomatic semantics in enforcing $\ecc$, $\ccc$, and $\scc$
consistency guarantess by ensuring that every reduction step preserves
correctness of axiomatic execution.

\begin{theorem}[Soundness preservation]
\label{lem:core-preservation}
Let $\E$ be a well-formed axiomatic execution state, and $\tau$ denote
a contract class.  If:
\begin{smathpar}
\E; \Theta; \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma \xhookrightarrow{\eff} \E'; \Theta';
\langle s,i,\sigma \rangle \Sigma'
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv_{\tau}[\eff/\cureff]$ 
\end{theorem}

>>>>

\subsection{Operational Semantics}
\renewcommand{\auxred}[4]{#1 \vdash #2 \;\xhookrightarrow{#3}\; #4 }

We now describe operational semantics of a data store that implements strong,
causal and eventual consistency guarantees. The semantics also serves as an
elegant representation of our implementation of \name.

@@

The state of an operational execution ($\E$) is a tuple $\Exec$ where
$\EffSoup$ is a set of effects, and $\visZ,\soZ, \sameobjZ \subseteq \EffSoup
\times \EffSoup$ are \emph{visibility}, \emph{session order}, and \emph{same
object} relations over effects, respectively. We concretize an effect ($\eff$)
as a tuple $(s,i,op,v)$, which records the fact that $i^{th}$ action in session
with {\sf SessID} $s$, which is an operation $op$ on the replicated object, has
been successfully executed on some replica yielding a return value $v$. Note
that the combination of $s$ and $i$ uniquely identifies the effect. Session
order relation ($\soZ$) relates effects generated by the same session. An
effect $\eff = (s,i,op,v)$ is said to precede another effect $\eff' =
(s',i',op',v')$ in session order if and only if $s'=s$ and $i'\ge i$. Since we
only consider one replicated object in our formalization, the $\sameobjZ$
relation relates every pair of effects in the effect soup ($\EffSoup$). An
effect generated at a replica becomes visible at rest of the replicas
eventually.  If we denote the effect generated by the operation $op$ as
$\eff_{op}$, then $\Theta(r) \times \{\eff_{op}\} ~\subseteq~ \visZ$. Often, in
our formalization, we use $\visZ$ and $\soZ$ binary relations to obtain a set
of effects visible to a given effect $\eff$, or set of effects that precede a
given effect $\eff$ in the session order. As a syntactic convenience, whenever
$R$ is a binary relation, we write $R(\eff)$ to denote the set of all $\eff'$
such that $(\eff,\eff') \in R$.  Conversely, we write $R^{-1}(\eff)$ to denote
the set of all $\eff'$ such that $(\eff',\eff) \in R$.

@@

\subsection{Soundness of Operational Semantics}

Our main meta-theoretic result guarantees the soundness of our operational
semantics in enforcing $\ecc$, $\ccc$, and $\scc$ consistency guarantess by
ensuring that every reduction step preserves correctness of operational
execution.

\begin{theorem}[Soundness preservation]
\label{lem:core-preservation}
Let $\E$ be a well-formed operational execution state, and $\tau$ denote a
contract class.  If:
\begin{smathpar}
\E; \Theta; \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma \xhookrightarrow{\eff} \E'; \Theta';
\langle s,i,\sigma \rangle \Sigma'
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv_{\tau}[\eff/\cureff]$
\end{theorem}
